---
title: "missing_value"
author: "Hanying Ji - hj2473"
date: "2018/11/25"
output: html_document
---
## Types of Missing Values

MCAR, MAR, and NMAR.

1. MCAR (Missing Completely At Random) 
No cause to the missingness

2. MAR (Missing At Random)
the values which are missing can be completely explained by the data we already have. For example, there may be a case that Males are less likely to fill a survey related to depression regardless of how depressed they are. Categorizing missing values as MAR actually comes from making an assumption about the data and there is no way to prove whether the missing values are MAR. Whenever the missing values are categorized as MAR or MCAR and are too large in number then they can be safely ignored.

3. (NMAR)Not Missing At Random
The fact that a person???s spouse name is missing can mean that the person is either not married or the person did not fill the name willingly. Thus, the value is missing not out of randomness and we may or may not know which case the person lies in. Who knows, the marital status of the person may also be missing!

## Numeric
Imputed with mean value
Imputed by group

## Categorical
Imputed by mode

## Other situation
Imputed with zeros or very large values (so that they can be differentiated from the rest of the data) 
Imputed with value that falls outside the range of values

## R package: mice
```{r}
library(mice)
library(lattice)
data(nhanes)
# first look at data
str(nhanes)
# plot the missing value
nhanes_miss = aggr(nhanes, col=mdc(1:2), numbers=TRUE, sortVars=TRUE, labels=names(nhanes), cex.axis=.7, gap=3, ylab=c("Proportion of missingness","Missingness Pattern"))
```
52% data no missing value, 28% data miss chl+bmi+hyp+age, 12% data miss chl only??????

```{r}
mice_imputes = mice(nhanes, m=5, maxit = 40) # m: the number of times the model should run
                                            # matix: Every dataset was created after a maximum of 40 iterations
# mice_imputes$method
Imputed_data=complete(mice_imputes,5) #use the 5th dataset to impute the original one
```